Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-02 rapport.tex
minor changes

		One important thing to consider for practical implementations of attacks is the memory footprint. There exist a lot of algorithms that are either galactic, i.e. that have good asymptotic complexity but will never be used in practice because of big-Oh factors, famous examples of galactic algorithms are matrix multiplication in $\mathcal{O}(n^2.371552)$ \cite{WXXZ23} or integer multiplication in $\mathcal{O}(nlog(n))$ \cite{HH21}. Other algorithms can be very practical but necessitate a huge amount of memory like birthday attacks or rainbow table attacks on hash functions thus making them impractical.

>>>>

		One important thing to consider for practical implementations of attacks is the memory footprint. There exist a lot of algorithms that are either galactic, i.e. that have good asymptotic complexity but will never be used in practice because of big-Oh factors, famous examples of galactic algorithms are matrix multiplication in $\mathcal{O}(n^{2.371552})$ \cite{WXXZ23} or integer multiplication in $\mathcal{O}(nlog(n))$ \cite{HH21}. Other algorithms can be very practical but necessitate a huge amount of memory like birthday attacks or rainbow table attacks on hash functions thus making them impractical.
